toyData

### 2021-10-07 latex/dataMaid_toyData.Rmd
Update to keep on CRAN

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2017-11-14 13:41:55
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

----------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character    factor    labelled   numeric    integer    logical     Date   
----------------------------------------------------- ----------- ---------- ---------- ---------- ---------- --------- ----------
Identify miscoded missing values                       $\times$    $\times$   $\times$   $\times$   $\times$

@@

 *  Created by Claus Thorn Ekstrøm.

 *  Report creation time: Tue Nov 14 2017 13:41:55

 *  dataMaid v1.0.1 [Pkg: 2017-11-13 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.2 (2017-09-28).

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.1).

>>>>

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: 2018-04-11 01:02:39
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

@@

----------------------------------------------------------------------------------------------------------------------------------
&nbsp;                                                 character    factor    labelled   numeric    integer    logical     Date   
----------------------------------------------------- ----------- ---------- ---------- ---------- ---------- --------- ----------
Identify miscoded missing values                       $\times$    $\times$   $\times$   $\times$   $\times$             $\times$

@@

 *  Created by Claus Thorn Ekstrøm (username: `cld189`).

 *  Report creation time: Wed Apr 11 2018 01:02:39

 *  Report Was run from directory: `/Users/cld189/ku/R/cleanR/latex`

 *  dataMaid v1.1.0 [Pkg: 2018-03-02 from local (ekstroem/dataMaid@NA)]

 *  R version 3.4.4 (2018-03-15).

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS High Sierra 10.13.3).
